### 2022-12-05 lmcs/introduction.tex
*reflection -> operational correspondence

In the $\pi$-calculus literature, there have been several attempts at developing Curry-Howard correspondences between session-typed $\pi$-calculus and linear logic~\cite{girard87}: Caires and Pfenning's $\pi$DILL~\cite{cairespfenning10} corresponds to dual intuitionistic linear logic~\cite{barber96}, and Wadler's Classical Processes~\cite[CP]{wadler14} corresponds to classical linear logic~\cite[CLL]{girard87}. Both calculi guarantee deadlock freedom, which they achieve by restricting structure of processes and shared channels to \emph{trees}, by combining name restriction and parallel composition into a single construct, corresponding to the logical cut. This ensures that two processes can only communicate via exactly one series of channels, which rules out interleavings of sessions, and guarantees deadlock freedom.
There are many downsides to combining name restriction and parallel composition, such as lack of modularity, difficulty typing structural congruence and formulating label-transition semantics, which have led to various approaches to decoupling these constructs. Hypersequent CP~\cite{MP18,kokkemontesi19popl,kokkemontesi19tlla} and Linear Compositional Choreographies~\cite{CarboneMS18} decouple them, but maintain the correspondence to linear logic and allow only tree-structured processes. Priority CP~\cite[PCP]{dardhagay18extended} weakens the correspondence to CLL in exchange for a more expressive language which allows cyclic-structured processes. PCP decouples CP's cut rule into two separate constructs: one for parallel composition via a mix rule, and one for name restriction via a cycle rule. To restore deadlock freedom, PCP uses \emph{priorities}~\cite{kobayashi06,padovani14}. Priorities encode the \emph{order of actions} and rule out bad cyclic interleavings. Dardha and Gay~\cite{dardhagay18extended} prove cycle-elimination for PCP, adapting the cut-elimination proof for classical linear logic, and deadlock freedom follows as a corollary.

CP and GV are related via a pair of translations which satisfy simulation~\cite{lindleymorris16}, and which can be tweaked to satisfy reflection. The two calculi share the same strong guarantees. GV achieves deadlock freedom via a similar syntactic restriction: it combines channel creation and thread spawning into a single operation, called ``fork'', which is related to the cut construct in CP. Unfortunately, as with CP, this syntactic restriction has its downsides.

>>>>

In the $\pi$-calculus literature, there have been several attempts at developing Curry-Howard correspondences between session-typed $\pi$-calculus and linear logic~\cite{girard87}: Caires and Pfenning's $\pi$DILL~\cite{cairespfenning10} corresponds to dual intuitionistic linear logic~\cite{barber96}, and Wadler's Classical Processes~\cite[CP]{wadler14} corresponds to classical linear logic~\cite[CLL]{girard87}. Both calculi guarantee deadlock freedom, which they achieve by restricting the structure of processes and shared channels to \emph{trees}, by combining name restriction and parallel composition into a single construct, corresponding to the logical cut. This ensures that two processes can only communicate via exactly one series of channels, which rules out interleavings of sessions, and guarantees deadlock freedom.
There are many downsides to combining name restriction and parallel composition, such as lack of modularity, difficulty typing structural congruence and formulating label-transition semantics, which have led to various approaches to decoupling these constructs. Hypersequent CP~\cite{MP18,kokkemontesi19popl,kokkemontesi19tlla} and Linear Compositional Choreographies~\cite{CarboneMS18} decouple them, but maintain the correspondence to linear logic and allow only tree-structured processes. Priority CP~\cite[PCP]{dardhagay18extended} weakens the correspondence to CLL in exchange for a more expressive language which allows cyclic-structured processes. PCP decouples CP's cut rule into two separate constructs: one for parallel composition via a mix rule, and one for name restriction via a cycle rule. To restore deadlock freedom, PCP uses \emph{priorities}~\cite{kobayashi06,padovani14}. Priorities encode the \emph{order of actions} and rule out bad cyclic interleavings. Dardha and Gay~\cite{dardhagay18extended} prove cycle-elimination for PCP, adapting the cut-elimination proof for classical linear logic, and deadlock freedom follows as a corollary.

CP and GV are related via a pair of translations which satisfy simulation~\cite{lindleymorris16}, and which can be tweaked to satisfy operational correspondence. The two calculi share the same strong guarantees. GV achieves deadlock freedom via a similar syntactic restriction: it combines channel creation and thread spawning into a single operation, called ``fork'', which is related to the cut construct in CP. Unfortunately, as with CP, this syntactic restriction has its downsides.
